\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem, hyperref, titlesec, fontawesome, xcolor, tabularx}
\renewcommand{\familydefault}{\sfdefault}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}
\pagestyle{empty}

% Header
\begin{center}
    {\LARGE\textbf{Zishan Ahamed Thandar}}\\
    City, Country | +91 XXXXX XXXXX | \href{mailto:email@example.com}{email@example.com}\\
    \href{https://linkedin.com/in/username}{LinkedIn} | \href{https://portfolio.example.com}{Portfolio}
\end{center}

\section*{Summary}
Cybersecurity Professional with expertise in penetration testing, vulnerability assessment, and security analysis. Specialized in risk mitigation, cloud security, and API security testing. Strong problem-solving skills with a passion for securing digital assets.

\section*{Education}
\begin{tabularx}{\linewidth}{X r}
    \textbf{Bachelor of Technology, University Name} & Year - Year \\
    Relevant Course 1, Institution & Year \\
    Relevant Course 2, Institution & Year 
\end{tabularx}

\section*{Technical Skills}
\textbf{Security Tools:} Security tool 1, Security tool 2, Security tool 3, Security tool 4.\\
\textbf{Pentesting:} Web Security, API Security, Cloud Security, Network Security.\\
\textbf{Operating Systems:} Linux (Kali, Ubuntu), Windows.\\
\textbf{Programming Languages:} Python, Bash, JavaScript, SQL.

\section*{Professional Experience}
\begin{tabularx}{\linewidth}{X r}
    \textbf{Security Researcher, Company Name} & Year - Present \\
\end{tabularx}
\begin{itemize}
    \item Performed security testing, vulnerability analysis, and risk assessments.
    \item Identified and reported security vulnerabilities in web and mobile applications.
    \item Developed automated security tools to improve assessment efficiency.
\end{itemize}

\begin{tabularx}{\linewidth}{X r}
    \textbf{Penetration Tester, Company Name} & Year - Year \\
\end{tabularx}
\begin{itemize}
    \item Conducted penetration tests on networks, applications, and cloud environments.
    \item Provided detailed security reports with remediation steps for clients.
    \item Assisted organizations in implementing secure coding practices.
\end{itemize}

\section*{Certifications}
\begin{tabularx}{\linewidth}{X r}
    Certified Red Team Professional (CRTP) & Year \\
    Offensive Security Certified Professional (OSCP) & Year \\
    Security Certification 1 & Year \\
\end{tabularx}

\section*{Languages}
\begin{itemize}
    \item German (Fluent)
    \item English (Proficient)
    \item Arabic (Basic)
\end{itemize}

\end{document}
